Revisiting the Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation using complex Empirical Orthogonal Functions

### 2021-08-12 analysis/paper/shceof.Rmd
Pasa a break a oración

One typical way of describing the zonally asymmetric circulation is by the amplitude and phase of zonal waves obtained by Fourier decomposition of geopotential height at each latitude [e.g.
@vanloon1972;@trenberth1980;@turner2017].
This approach suggests that zonal waves 1 and 3 explained most of the variance of the tropospheric extratropical Southern Hemisphere circulation (@vanloon1972).
However, this methodology relies on the assumption that the circulation can be meaningfully understood in terms of zonal waves of constant amplitude along a latitude circle.
This is not valid for meridionally propagating waves or zonal waves with localised amplitudes.
In the case of the wave 3, for example, @trenberth1985 observed that it played a role in blocking events, but this was mostly due to increased amplitude of a longitudinally localised wave train instead of an hemispheric-scale zonal wave 3.

@@

## cEOFs relationship with known modes of variability {#other-variables}
### SAM

@@

(ref:australia-pp-phase-cap) Same as Figure \@ref(fig:enso-phase) but for precipitation anomalies averaged between `r knitr::combine_words(LonLabel(box_australia$lon))` and `r knitr::combine_words(LatLabel(box_australia$lat))` (box shown in Figure \@ref(fig:pp-oceania) column b) in $\frac{\mathrm{mm}}{\mathrm{day}}$. 
Black line is the fit precipitation ~ sin(phase) + cos(phase) computed by weighted OLS using the magnitude of the cEOF2 as weights.

>>>>

One typical way of describing the zonally asymmetric circulation is by the amplitude and phase of zonal waves obtained by Fourier decomposition of geopotential height at each latitude [e.g. @vanloon1972; @trenberth1980; @turner2017].
This approach suggests that zonal waves 1 and 3 explained most of the variance of the tropospheric extratropical Southern Hemisphere circulation (@vanloon1972).
However, this methodology relies on the assumption that the circulation can be meaningfully understood in terms of zonal waves of constant amplitude along a latitude circle.
This is not valid for meridionally propagating waves or zonal waves with localised amplitudes.
In the case of the wave 3, for example, @trenberth1985 observed that it played a role in blocking events, but this was mostly due to increased amplitude of a longitudinally localised wave train instead of an hemispheric-scale zonal wave 3.

@@

## cEOFs relationship with known modes of variability {#other-variables}

### SAM

@@

(ref:australia-pp-phase-cap) Same as Figure \@ref(fig:enso-phase) but for precipitation anomalies averaged between `r knitr::combine_words(LonLabel(box_australia$lon))` and `r knitr::combine_words(LatLabel(box_australia$lat))` (box shown in Figure \@ref(fig:pp-oceania) column b) in $\frac{\mathrm{mm}}{\mathrm{day}}$. Black line is the fit precipitation \~ sin(phase) + cos(phase) computed by weighted OLS using the magnitude of the cEOF2 as weights.
